\documentclass{article}

\usepackage{microtype,amssymb,enumitem,color}
\usepackage[margin=1in]{geometry}
\usepackage[pdfborder={0 0 0},pdfauthor={Anthony Mendes, Cal Poly San Luis Obispo}]{hyperref}

% These next four lines require comiling with xelatex.  Remove to use pdflatex.
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella}
\setmonofont{InconsolataGo-Regular}
\setsansfont{AvenirLTStd-Book}

\setlist[enumerate]{itemsep=-1ex,topsep=0ex,parsep=1ex}
\setlist[itemize]{itemsep=-1ex,topsep=0ex,parsep=1ex}
\setlength{\parindent}{0ex}
\setlength{\parskip}{0ex}

\newcommand{\gdot}{~ {\color{green}$\bullet$} ~}

\definecolor{green}{RGB}{3,86,66}
\definecolor{gold}{RGB}{180,167,108}
\def\labelitemi{\color{green}$\bullet$}
\def\labelitemii{\color{green}$\circ$}

\newcommand{\sectionrule}[1]{\bigskip \smallskip
{\color{green} \begin{large} \textbf{#1} \end{large}} \\[-1.5ex]
{\color{gold} \rule{.8\textwidth}{.1mm}}
\smallbreak}

\pagestyle{empty}

\begin{document}

\begin{center}
{\begin{Huge}\color{green} \textbf{Anthony Mendes}\end{Huge}}

\medskip

\textsf{aamendes@calpoly.edu}
\gdot
\href{http://www.calpoly.edu/~aamendes}{\textsf{www.calpoly.edu/$\sim$aamendes}}
\gdot
\textsf{\begin{small}(805)756-1699\end{small}}
\gdot
\textsf{San Luis Obispo, CA}
\end{center}

\sectionrule{Objective}

Secure a data scientist position with an innovative organization in the San Francisco bay area.

\sectionrule{Education}

\textbf{Bachelor of Science in Mathematics}, Spring 2018 (expected) \\
Cal Poly, San Luis Obispo, California.

\medskip

Relevant course work includes advanced courses on
\begin{itemize}
\item Data Science
\item Numerical Analysis
\item Matrix and Linear Algebra
\item Nonparametric and Parametric Statistics
\item Design and Analysis of Algorithms
\end{itemize}

\medskip

Senior project analyzed Neilsen television ratings data from the Tennis Channel to determine
which tennis matches would yield the highest ratings.  The project involved significant
data processing, computer programming, various regression models, and the singular value
decomposition.

\sectionrule{Employment}

\textbf{Intern Software Developer}, Summer 2017 \\
Amazon-SLO, San Luis Obispo, CA

\smallskip

Responsible for preparing data acquired from user shipping addresses in order to decide the
optimal locations for new shipping centers.

\bigskip

\textbf{Research assistant}, Summer 2016 \\
Mathematics Department, Cal Poly, San Luis Obispo, CA.

\smallskip

Hand selected to work in a paid summer research position under the direction of Professor Smith.
Our project was to investigate the relationship between the Robinson Schensted algorithm and
a theorem concerning permutation inversions.

\bigskip

\textbf{Workshop Leader}, 2015--2017 \\
Mathematics Department, Cal Poly, San Luis Obispo, CA.

\smallskip

Led discussion sections for students in Calculus I, II, and III.  Consistently rated by students
as excellent with clear communication skills.

\sectionrule{Technical Skills}

\begin{itemize}
\item Python with pandas and scikit-learn
\item \LaTeX{}
\item Significant formal training in mathematics
\item Some experience with Java, C++
\end{itemize}

\sectionrule{Activities}

\begin{itemize}
\item Society of Women Engineers, 2014--2017
\item Math Club, 2014--2017
\item Cal Poly Active Minds club, 2014--2016
\item Dorm resident advisor, 2014--2015
\item Piano enthusiast
\end{itemize}

\end{document}

