\documentclass{article}

\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftitle = {Cal Poly Math 351}, pdfauthor = {Tony Mendes}, pdfsubject = {Typesetting}, colorlinks = true, urlcolor = blue, linkcolor = blue, citecolor = blue]{hyperref}

\usepackage{makeidx} 
\makeindex

\newtheorem{theorem}{Theorem}

\title{Automatic labels}
\author{Math 351}
\date{}

\begin{document}

\maketitle

\begin{abstract}
  This is an example of a abstract.  \index{abstract} An abstract is a short description of the contents of the document.  As a general rule, abstracts should be no more than a few sentences for papers and a few paragraphs for books.  This document contains examples on how to use \LaTeX{'s} self
numbering and labeling features.
\end{abstract}

\tableofcontents

\section{Introduction}

This document is designed to illustrate \LaTeX{'s} ability to self number sections, subsections,
theorems, equations, and so on.  We will also illustrate appendices, bibliographies, indices, and
footnotes.\footnote{Yes, even footnotes!  Oh, lucky day!}  Footnotes \index{footnotes} are created
using \verb~\footnote{text}~ and, if appearing at the end of a sentence, should appear after
the period.

\subsection{Run \LaTeX{} more than once}

Auxiliary files are created the first time \LaTeX{} is run.  These files store information about
labels and page numbers.  The next time \LaTeX{} is run, those files are referenced to create the 
table of contents, section numbers, and theorem numbers.  Because of this, \LaTeX{} must be run 
two or three times in order to properly display the labels.  Some bundled \LaTeX{} software do this 
automatically for you.  The output shown by the compiler may 
warn you if it appears that \LaTeX{} should be run again.

Sections \index{sections} are created with \verb~\section[TOC name]{Section Name}~, where the optional
\verb~[TOC name]~ string changes the name of the section in the table of contents.
There is also a similar \index{subsections} \verb~\subsection~ command.  To print a section without a number which
will not appear in the table of contents, use \verb~\section*{Section Name}~.  Then, to create
the table of contents, include the \verb~\tableofcontents~ command.  

\subsection[BibTeX]{Bibliographies using BibTeX}

Bibliographies can created with BibTeX.  \label{bibliographies}  \index{BibTeX} To do this, follow these
instructions (which have been auto-magically numbered using \index{enumerate} the \verb~enumerate~ environment): 
\begin{enumerate}
\item create a new file called \verb~file.bib~.
\item In that new file, create or copy and paste bibliography entries in the BibTeX format.  
Examples of the format can be found in the sample .bib file on our web site.  Even better, 
bibliography entries can be copy and pasted from \url{http://scholar.google.com}, or from other
paper indexing services such as MathSciNet.  BibTeX entries can also be found using an ISBN at 
\url{http://www.ottobib.com/}.  I will show this in class.
\item Cite authors or works using \verb~\cite{name1, name2}~.  For example, some of Leonhard 
Euler's \index{Euler} works include \cite{euler1741solutio,euler1759force}.  Later, Euler published 
\cite{euler1775meditationes}.
\item Place these two lines in the \LaTeX{} file (usually towards the end of the file) before
  the \verb~\end{document}~ command:
\begin{verbatim}
\bibliography{file}
\bibliographystyle{alpha} 
\end{verbatim}
Other choices for the bibliography styles are: 
\verb~abbrv~, \verb~acm~, \verb~alpha~, \verb~apalike~, \verb~ieeetr~, \verb~plain~, and 
\verb~siam~.
\item Run the following four commands one after the other in a terminal:
\begin{verbatim}
pdflatex file.tex
bibtex file
pdflatex file.tex
pdflatex file.tex
\end{verbatim}
The \verb~bibtex file~ command does not use the \verb~.bib~ extension.  Some \LaTeX{ing}
software may have other ways to compile.  Check the pull-down menus; look for something 
like \verb~pdflatex+bibtex~.
\end{enumerate}

\subsection{Creating an index} 

To create an \index{index} index, place these two lines before the \verb!\begin{document}! command:
\begin{verbatim}
\usepackage{makeidx} 
\makeindex 
\end{verbatim}

Mark words for inclusion in an index using the \verb~\index{word}~ command.  The page 
reference will appear on the same page that the \verb~\index{word}~ command is located.
There are variations on the \verb~\index~ command which can be used to change how the entries 
appear in the index; such options are found on page 87 of the text.  

Similar to BibTeX, the index must be compiled with its own command.  To compile an index, these
run these commands:
\begin{verbatim}
pdflatex file.tex
makeindex file
pdflatex file.tex
pdflatex file.tex
\end{verbatim}
The \verb~makeindex~ command does not use the \verb~.tex~ extension.  Some \LaTeX{ing}
software may have other ways to compile an index.  Check the pull-down menus;
look for something like \verb~pdflatex+makeindex+bibtex~.

\section{Referencing other parts of the text}

To mark a location in the text for future reference, insert \verb~\label{name}~.
The names for each of the labels in the document must be unique.  To reference this label,
use the command \verb~\ref{name}~ to reference the section (or subsection) and use the
\verb~\pageref{name}~ to reference the page.  For example, we showed how to include bibliographies
in section \ref{bibliographies} on page \pageref{bibliographies}. 

\subsection{Referencing in math mode}

Cross-referencing is \index{cross-referencing} enhanced by the standard \verb~amssymb~, \verb~amsmath~, and \verb~amsthm~
packages.  To create a numbered displayed equation in mathematics mode, use
\verb~\begin{equation}..\end{equation}~ instead of the usual \verb`\[..\]`.  The 
the \verb~\label{name}~ command must appear between
the \verb~\begin{equation}~ and \verb~\end{equation}~ commands.  When later referring to an equation,
the command \verb~\eqref{name}~ produces parentheses around the equation number. 

For example, the following identity can be proved using polar coordinates:
\begin{equation}
\label{Gauss}
\int_{-\infty}^\infty e^{-x^2} \, dx = \sqrt{\pi}.    
\end{equation}
The integral in \eqref{Gauss} is known as the Gaussian integral.

Differently named \verb~\label~ commands can be placed in each line in either the \verb~align~ or
\verb~multline~ environments.  To suppress a line number when using these environments, place
the \verb~\nonumber~ command somewhere on that line.  Instead of a line number, a word or
symbol can be placed in parenthesis on the side of an \verb~align~ or \verb~multline~ command
using \verb~\tag{word}~.\footnote{Use this sparingly, if ever!}

For an example of this, we have
\begin{align}
  \left( \int_{-\infty}^\infty e^{-x^2} \, dx \right)^2
  & = \iint_{\mathbb{R}^2} e^{-(x^2+y^2)} \, d(x,y) \tag{$\star$} \label{over the plane} \\
  & = \int_0^{2 \pi} \int_0^\infty e^{-r^2} r \, dr \, d\theta \label{polar} \\
  & = 2 \pi \int_{-\infty}^0 \frac{1}{2} e^u \, du \tag{$u = -r^2$} \\
  & = \pi, \nonumber
\end{align}
where we integrated over the plane $\mathbb{R}^2$ in \eqref{over the plane} and switched into polar
coordinates in \eqref{polar}.

Whenever you have a equation number in the document, you are telling the reader ``remember where
this line is!'', and so it is polite to suppress equation numbers unless those equations are
actually referenced in the document.

\subsection{Theorems and proofs}

Theorems, lemmas, exercises, and the like can be created using these steps. 
\begin{enumerate}
\item Place \verb~\newtheorem{name1}{Name2}~ before the \verb~\begin{document}~.
  The first name, \verb~name1~, is the environment name and will only used internally in the \LaTeX{}
  document.  The section name, \verb~name2~, will actually be printed, along with a number.
\item Create a theorem-like statement using the syntax
\begin{center}
  \verb~\begin{name1}[optional] ..text.. \end{name1}~.
\end{center}
\end{enumerate}
For example, we display theorem \ref{E} next.
\begin{theorem}[Euler]
\label{E}
If $t$ is a real number, then $e^{i t} = \cos t + i \sin t$.  \index{Cosine} \index{Sine}
\end{theorem}

Those wanting more control over the appearance of the theorem environment are referred to page
72 in the text.

The proof of this theorem can be written between \verb~\begin{proof}~ and \verb~\end{proof}~ statements.  This will automatically generate an end of proof symbol.  The placement of the end of proof
symbol can be manipulated using \verb~\qedhere~.\footnote{See page 72 of the text.}
Here is an example of the proof environment, which serves as a proof of Euler's \index{Euler} Theorem, our Theorem \ref{E}. 

\begin{proof}
Using the power series \index{power series} for $e^{i t}$, \index{Exponential function} 
\begin{align*}
  e^{i t} & = 1 + \frac{(i t)^1}{1!} + \frac{(i t)^2}{2!} 
  + \frac{(i t)^3}{3!} + \frac{(i t)^4}{4!} + \cdots \\
  & = 1 + i \frac{t^1}{1!} - \frac{t^2}{2!} - i \frac{t^3}{3!} + \frac{t^4}{4!} + \cdots \\
  & = \left( 1 - \frac{t^2}{2!} + \frac{t^4}{4!} - \cdots \right)
  + i \left( t - \frac{t^3}{3!} + \frac{t^5}{5!} - \cdots \right), 
\end{align*}
which, using the power series for $\cos t$ and $\sin t$, is equal to $\cos t + i \sin t$. 
\end{proof}

\appendix

\section{Appendix}

All appendix \index{appendix} material must appear between a \verb~\appendix~ command but before
the \verb~\end{document}~ command.   After that,  include any appendix sections with
the usual \verb~\section{Section Name}~ command. 

\bibliography{351Labels}
\bibliographystyle{alpha} 

\printindex

\end{document}
